|

### 2024-04-22 manuscript.Rmd
Testing full build with bootstrapping

processdata <- 1  # this flag determines the amount of processing, with 3 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data (requires 120MB of storage)
# 2 - do statistics and bootstrapping using processed data

@@

  comparisons <- matrix(c(1,2,1,3,2,3),nrow=3,ncol=2,byrow=TRUE)

@@

  for (s in 1:29){
    data <- readMat(paste0('local/RawData/Experiment 1/',s+300,'/',s+300,'trialorderRobots.mat'))

@@

@@

  for (s in 1:30){
    data <- readMat(paste0('local/RawData/Experiment 2/',s+350,'/trialorderMasks.mat'))

>>>>

processdata <- 2  # this flag determines the amount of processing, with 3 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data (requires 120MB of storage)
# 2 - do statistics and bootstrapping using processed data

@@

  if (!file.exists('local/robotsmvpa/301_101.mat')){
  osfproject <- osf_retrieve_node('uzbns')
  osffiles <- osf_ls_files(osfproject)
  fid <- which(osffiles$name=='robotsmvpa.zip')
  osf_download(osffiles[fid,], path='local/',progress=TRUE)
  unzip('local/robotsmvpa.zip',exdir='local/',overwrite=TRUE)
  }
  if (!file.exists('local/responsedata/301trialorderRobots.mat')){
  osfproject <- osf_retrieve_node('uzbns')
  osffiles <- osf_ls_files(osfproject)
  fid <- which(osffiles$name=='responsedata.zip')
  osf_download(osffiles[fid,], path='local/',progress=TRUE)
  unzip('local/responsedata.zip',exdir='local/',overwrite=TRUE)
  }
  comparisons <- matrix(c(1,2,1,3,2,3),nrow=3,ncol=2,byrow=TRUE)

@@

  for (s in 1:29){
    data <- readMat(paste0('local/responsedata/',s+300,'trialorderRobots.mat'))

@@

  if (!file.exists('local/masksmvpa/351_101.mat')){
  osfproject <- osf_retrieve_node('uzbns')
  osffiles <- osf_ls_files(osfproject)
  fid <- which(osffiles$name=='masksmvpa.zip')
  osf_download(osffiles[fid,], path='local/',progress=TRUE)
  unzip('local/masksmvpa.zip',exdir='local/',overwrite=TRUE)
  }
  if (!file.exists('local/responsedata/351trialorderMasks.mat')){
  osfproject <- osf_retrieve_node('uzbns')
  osffiles <- osf_ls_files(osfproject)
  fid <- which(osffiles$name=='responsedata.zip')
  osf_download(osffiles[fid,], path='local/',progress=TRUE)
  unzip('local/responsedata.zip',exdir='local/',overwrite=TRUE)
  }

@@

  for (s in 1:30){
    data <- readMat(paste0('local/responsedata/',s+350,'trialorderMasks.mat'))
